Visual Search and Pre-crastination

### 2023-09-01 RegReport/paper.tex
Finished registered analysis

\begin{figure}[t]
  \centering  
 % \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/prior_plot.pdf}}
%  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/post_plot.pdf}}
  \caption{(a) Prior and (b) posterior distributions for the mean of the two groups of participants, and the difference between them. Our priors for the two groups are identical, hence the overlapping distributions.}
  \label{fig:full_exp_strategy}
\end{figure}

Our final registered hypothesis concerns the relationship between pre-crastination and conscientiousness. In line with the visual search analysis, we treated precrastination as a binary variable (excluding intermediate participants). The results of which are displayed in Figure X. As is clear from the figure, there is little difference in conscientiousness between people who consistently precrastinated in the bucket task versus those who consistently picked up the farther bucket first. Because this is inconsistent with previous results, to be more confident in this result we ran a second analysis with precrastination coded from 0 to 6, in terms of how many trials on which the participant precrastinated. The results were...  [DOES THAT WORK...?]

>>>>

\begin{figure}[t]
  \centering

\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/post_plot.pdf}}
\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pre_cras_consc.pdf}}
  \caption{(a) Posterior distributions for the mean of the two groups of participants, and the difference between them. (b) There is no evidence for a relationship between pre-crastination and conscientiousness}
  \label{fig:full_exp_strategy}
\end{figure}

Our final registered hypothesis concerns the relationship between pre-crastination and conscientiousness. We find no evidence for this relationship in our data. This holds whether we continue to treat pre-crastination as a binary variable ($95\%$ HPDI = [-0.19, 0.17] for the difference between groups) or as a continuous variable and measure the number of trials out of six in which participants pre-crastinated ($95\%$ HPDI = [-0.03, 0.03] for the effect of number of trials on conscientiousness).

### 2023-09-01 analysis/2_registered.Rmd
more work on analysis
Finished registered analysis

```{r, message=FALSE}
# attach packages
#library(rethinking)
library(tidyverse)
library(patchwork)
library(binom)
```

@@

>>>>

```{r, message=FALSE}
# attach packages
library(rethinking)
library(tidyverse)
library(patchwork)
library(binom)
```

@@

# Registered Analysis

## Main Hypothesis

Is there a link betweeen pre-crastination and visual search strategy

### Pilot Data

First, we will rerun the model with the old pilot data. This is to double check the analysis pipeline is working properly.

```{r, results = "hide", message=FALSE, results = "hide"}
source("my_model_functions.R")

d_pilot <- read_csv("../pilot_experiment/level3_summary.csv",
                    show_col_types = FALSE) %>%
  mutate(pre_crastinate = as_factor(
    ifelse(pre_crastinate == 0, "no", "yes"))) %>%
  rename(search_strat = "opt_strat")

m_pilot <- fit_model(d_pilot)
```

```{r}
# generate prior only plot
plt <- gen_plot_pred(d_pilot, m_pilot, TRUE)
ggsave("scratch/pilot_prior_plot.pdf", plt, width = 5, height = 4)

plt2 <- gen_plot_pred(d_pilot, m_pilot)

plt + plt2
ggsave("scratch/pilot_plot.pdf", plt2, width = 5, height = 4)
```

### Full Data

Now run the model on the full data
```{r, results = "hide"}
d <- dat %>% select(prop_hard, pre_crastinate) %>%
  filter(pre_crastinate != "intermediate") %>%
  rename(search_strat = "prop_hard")

m_full <- fit_model(d)
```

```{r}
# generate prior only plot

plt <- gen_plot_pred(dat, m_full)
plt
ggsave("scratch/post_plot.pdf", plt + theme(legend.position = "none"), width = 4, height = 3)
```

# Now compute some summaries of the model posterior:

```{r}
samples <- rstan::extract(m_full)

pred_dat <- tibble(pre_crastinate = c(-0.5, 0.5))

X = as.matrix(pred_dat)
X <- cbind(1, X)

# Look at prior predictions for mmu
mu <- array(0, dim = c(100000, nrow(X)))
for (ii in 1:100000) {
	# generate a random beta from priors
	beta <- as.vector(c(
		rnorm(1, mean=0, sd=.5), 
		rnorm(1, mean=0, sd=.1)
		))
	mu[ii, ] <- plogis(X %*% beta)
}

mu_df <- tibble(
	pre_crastinate = rep(c("no", "yes", "difference"), each = 100000),
	mu  = c(mu[,1], mu[,2], mu[,2] - mu[,1]))

HPDI(mu[,2] - mu[,1], 0.95)
mean(abs(mu[,2] - mu[,1]) > 0.05)
mean((mu[,2] - mu[,1]) > 0)
```

## Pre-crastination & Conscientiousness

```{r}
my_cols <-  c(viridis::viridis(3)[1], "#444444", viridis::viridis(3)[3], viridis::viridis(3)[2],  "#999999")

dat_p %>% filter(!is.na(pre_crastinate), !is.na(conscientiousness)) %>%
  ggplot(aes(pre_crastinate, conscientiousness, fill = pre_crastinate)) + 
  geom_boxplot(alpha = 0.5) +
  scale_fill_manual("pre-crastinate", values = my_cols) -> plt

plt

ggsave("scratch/pre_cras_consc.pdf", plt+theme_bw(), width = 4, height = 3)

cor.test(dat_p$conscientiousness, dat_p$n_pc)

# now to it with Bayes
library(brms)
m <- brm(n_pc ~ conscientiousness, data = dat_p,
               priors = c(prior()))
